Comparing Different Planned Missingness Designs in Longitudinal Studies

### 2018-05-17 Documentation/manuscript.Rnw

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

<<misslow, fig.cap = "Low missingness", echo = FALSE, message = FALSE>>=
require(gridExtra)
grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
@

@@

<<echo=FALSE>>=
load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high.RData")
high <- d

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med.RData")
med <- d

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low.RData")
low <- d

library(xtable)
print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),type="latex", comment = FALSE)

>>>>

\begin{document}
%\SweaveOpts{concordance=TRUE}

@@

<<misslow, fig.cap = "Low missingness", echo = FALSE, message = FALSE, warning = FALSE, fig = TRUE>>=
require(gridExtra)
grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
@

@@

<<echo=FALSE, warning=FALSE>>=
# if (Sys.info()[8] == "Josie"){
#   setwd("~/GitHub/designedmissingness")
# }
# if (Sys.info()[8] == "gregorymatthews"){
#   setwd("~/Dropbox/designedmissingnessGit")
# }

# Table 7
library(kableExtra)
library(dplyr)
load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime0.RData")
high_8 <- d

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med_hightime0.RData")
med_8 <- d

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime0.RData")
low_8 <- d

c8 <- rbind(low_8[[1]],med_8[[1]],high_8[[1]],low_8[[2]],med_8[[2]],high_8[[2]],low_8[[3]],med_8[[3]],high_8[[3]])

df_8 <- data.frame(Design = rep(c("Split Form","Altered Split Form", "Wave Missingness"), each = 12), Missingness = rep(rep(c("Low","Medium", "High"), each = 4),3), Parameter = rep(c("$\\gamma_0$", "$\\beta_1$", "$\\beta_2$", "$\\beta_3$"),9), Bias = unlist(c8["Bias"]), unlist(c8["Pct Bias"]), MSE = unlist(c8["MSE"]), Coverage = c8["Coverage"], c8["CI Length"], FMI = c8["FMI"])

df_8[,4:9] <- apply(df_8[,4:9], 2, round, digits = 3)

names(df_8) <- c("Design", "Missingness", "Parameter", "Bias", "Pct Bias", "MSE", "Coverage", "CI Length", "FMI")
row.names(df_8) <- NULL
kable(df_8, escape = FALSE, format ="latex") %>%
  collapse_rows(columns = 1:2, latex_hline = "full")
  column_spec(1, width = "30em")

# library(knitr)
# kable(cbind("","","",rbind(low_8[[1]],med_8[[1]],high_8[[1]],low_8[[2]],med_8[[2]],high_8[[2]],low_8[[3]],med_8[[3]],high_8[[3]])),format="latex")
